Summary Tables

### 2022-10-21 summary_tables.Rmd
Correct number of scenarios

## Trip proportion
Case study specific trip proportions by mode, for baseline and five scenarios

@@

## Distance tables
Case study specific distance tables for baseline and five scenarios

@@

## Distance tables scaled by using total population (per year in km)
Case study specific distance tables for baseline and five scenarios

@@

Case study specific duration tables for baseline and five scenarios (per day in minutes)

>>>>

## Trip proportion
Case study specific trip proportions by mode, for baseline and four scenarios

@@

## Distance tables
Case study specific distance tables for baseline and four scenarios

@@

## Distance tables scaled by using total population (per year in km)
Case study specific distance tables for baseline and four scenarios

@@

Case study specific duration tables for baseline and four scenarios (per day in minutes)
